% Created 2023-07-23 Sun 18:59
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Anton Hibl}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Anton Hibl},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.5.5)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\section{Final Group Project Plan: Art Gallery Website}
\label{sec:orgff780d7}

\subsection{Team Members: Anton Hibl, Ethan Wilcox}
\label{sec:org24faf47}

\subsubsection{Introduction}
\label{sec:org38be2af}

This document provides an exhaustive, step-by-step plan for our Art Gallery
Website project, elaborating on our strategies and methods to bring the project
to life. By partitioning our project into two main phases, we aim to streamline
our progress while ensuring a thorough, complete, and high-quality result. 

\subsubsection{1. Detailed List of React Components and their Interactions}
\label{sec:org0e30339}

To establish clarity and a systematic approach, we have divided our components
into two categories - "core" and "supportive". Our core components are integral
for the main functionality of our application, while the supportive components
enrich user interaction and assist in managing the data handling process. 

\begin{itemize}
\item Core Components:

\begin{itemize}
\item Home
\item Gallery
\item ArtworkDetail
\item UserAccount
\item Navbar
\end{itemize}

\item Supportive Components:

\begin{itemize}
\item ArtworkCard
\item Search
\item LoginForm and RegisterForm
\end{itemize}
\end{itemize}

\subsubsection{2. Functions and Application Logic}
\label{sec:org7b21e39}

We have identified the core functions that will govern the primary operations of
our application: 

\begin{itemize}
\item User registration and authentication: Functions like registerUser, loginUser,
logoutUser will handle user registration and authentication. They will
interact with the LoginForm and RegisterForm components and update the state
of UserAccount and Navbar components.

\item Artwork handling: Functions like uploadArtwork, searchArtwork will manage
artwork-related operations. They will coordinate with the UserAccount, Home,
Gallery, and Search components for various use-cases.

\item User interactions: Functions like interactWithArtwork will handle user
interactions like liking, commenting, and sharing the artwork. They will
mainly interact with the ArtworkDetail component.
\end{itemize}

\subsubsection{3. API Request-Response Formats}
\label{sec:org5667352}

Our application will maintain consistent interaction with the backend using the
following primary endpoints:

\begin{itemize}
\item User Registration (POST /api/users)
\item User Login (POST /api/users/login)
\item Upload Artwork (POST /api/artworks)
\item Search Artwork (GET /api/artworks/search)
\item User Interactions (POST /api/interactions)
\end{itemize}

\subsubsection{4. Endpoint Routes}
\label{sec:org321e844}

Each of our API endpoint routes will serve a clear purpose and handle distinct
data operations. We have carefully selected and designed these routes to make
the process of data handling efficient, secure, and reliable. Each route and its
functionality, along with the expected data for each endpoint, have been
meticulously explained in our previous plan.

\subsubsection{5. Design References}
\label{sec:orge421bc7}

For the design of our Art Gallery Website, we are focusing on maintaining a
minimalist aesthetic while ensuring intuitive user navigation and high-quality
artwork showcase. Our design inspiration is drawn from established digital art
platforms and current web design trends to provide our users with a fresh,
contemporary, and enjoyable user experience. For each component and the overall
website design, we will create wireframes and mockups to provide a clear visual
guide during our development process.

\subsubsection{6. Phase-1 and Phase-2 Deliverables}
\label{sec:orgc10ff3b}

To ensure a manageable workload and efficient development process, we have
divided our project into two major phases. Each phase will focus on distinct
aspects of our project, allowing us to maintain an organized approach throughout
our development process.

\begin{itemize}
\item Phase-1 Deliverables:
\begin{itemize}
\item Project setup and environment preparation
\item Design and implementation of the database schema
\item Development of basic components and user registration/login functionalities
\item Initial API endpoints for user registration and login
\end{itemize}

\item Phase-2 Deliverables:
\begin{itemize}
\item Development of advanced components and functionalities
\item Additional API endpoints to handle artwork upload, search, and user interactions
\item Thorough testing, debugging, and deployment
\end{itemize}
\end{itemize}

\subsubsection{7. Task Breakdown and Member Allocation}
\label{sec:orgb313068}

Our project task breakdown is primarily divided between frontend and backend
development tasks. The roles and tasks assigned to each team member ensure a
fair distribution of workload and an effective division of responsibilities
based on each member's strengths and areas of expertise.

\begin{itemize}
\item Anton:

\begin{itemize}
\item Phase-1 Tasks:
\begin{itemize}
\item Environment Setup
\item Home Component Development
\item Navbar Component Development
\item LoginForm and RegisterForm Component Development
\item Design Wireframes and Mockups
\end{itemize}

\item Phase-2 Tasks:
\begin{itemize}
\item Gallery Component Development
\item ArtworkCard and ArtworkDetail Components Development
\item UserAccount Component Development
\item Testing and Debugging
\end{itemize}
\end{itemize}

\item Ethan:

\begin{itemize}
\item Phase-1 Tasks:
\begin{itemize}
\item Project Initialization
\item Database Schema Implementation
\item User Registration and Login API Endpoints
\item Initial Backend Testing
\end{itemize}

\item Phase-2 Tasks:
\begin{itemize}
\item Artwork Upload and Search API Endpoints
\item User Interaction API Endpoints
\item Backend Optimization
\item Final Backend Testing
\end{itemize}
\end{itemize}

\item Collaborative Tasks:

\begin{itemize}
\item Project Planning and Design
\item Component Integration
\item Project Review and Debugging
\item Final Project Deployment
\end{itemize}
\end{itemize}

\subsubsection{Conclusion}
\label{sec:orgbba319f}

In conclusion, this detailed plan and task breakdown ensure a systematic
approach to the project, efficient workload distribution, and effective
collaboration between team members. By adhering to this plan along with other
tools like our ER schema guidelines, we aim to deliver a high-quality, fully
functional Art Gallery Website within the allocated timeframe.
\end{document}