% Created 2023-07-31 Mon 10:50
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Anton Hibl}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Anton Hibl},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.5.5)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

\section{Phase-1 Report: A Comprehensive Technical Overview}
\label{sec:orge0c54d9}

\subsection{Introduction}
\label{sec:org93342ac}

Phase-1 of the project has laid a strong and nuanced foundation, driven by the
vision of delivering a high-quality, secure, and efficient product. This stage
was characterized by meticulous planning, thoughtful design, extensive testing,
and close connection between different facets of the development team. 

\subsection{Frontend Development}
\label{sec:orgf9fd8dd}

\subsubsection{Features and Functionalities}
\label{sec:orgd9ed703}

\begin{itemize}
\item User Registration and Login System: A robust user registration system was
developed with input validation, secure password handling using
cryptographic hashing, and a seamless user experience.

\item Art Gallery View: An intuitive and interactive art gallery view was
designed, with capabilities for users to browse, filter, and view artworks
in various arrangements.

\item Responsive Design: A mobile-first approach ensured that the user interface
would adapt across different devices and screen sizes.
\end{itemize}

\subsubsection{Design Components and Wireframes}
\label{sec:org387dad6}

The wireframes created during this phase provided a visual blueprint for the
interface design. Components were mapped out to ensure cohesion across different
sections of the application, with an emphasis on usability and aesthetics.

\subsection{Backend Development}
\label{sec:org6f146a8}

\subsubsection{Features and Functionalities}
\label{sec:org8caac8d}

\begin{itemize}
\item User Authentication and Authorization: Utilizing JWT tokens, a secure
authentication system was implemented, ensuring data integrity and user
privacy by protecting and hashing passwords.

\item UI: Navigation and homepage components were completed and will ensure a
complete and unified experience for visitors to the gallery.

\item Database Design: A simple yet effective ER schema was designed and translated
into JavaScript, which has established a solid foundation for data
relations and integrity.
\end{itemize}

\subsubsection{Secure Design Considerations}
\label{sec:org90278ff}

\begin{itemize}
\item Data Validation: Extensive validation rules were applied to prevent SQL
injections.

\item Encryption: Encryption and specifically hashing techniques were used to
secure sensitive data like passwords.
\end{itemize}

\subsection{Integration of Gulp}
\label{sec:org97131d2}
Gulp was integrated into the workflow, providing automation for repetitive tasks
such as minification, compilation, unit testing, and linting. This not only
streamlined the development process but also ensured consistent code quality;
now we are able to ensure the build system stays the same across the local and
remote environments and ensure all changes work immediately after they are
pushed. Overall this helps debugging and reduces time to solve issues in our
experience.

\subsection{Test-Driven Development (TDD)}
\label{sec:org560ad7e}
Through TDD, a detailed suite of tests was developed using Jest and
Supertest:

\begin{itemize}
\item Unit Tests: For individual functions and methods.

\item Integration Tests: To test interactions between different parts of the
application.

\item End-to-End Tests: To simulate real user scenarios and test the application
as a whole.
\end{itemize}

The continuous testing cycle facilitated early detection of issues and robust
code quality. We specifically use two suites to test either the front-end(jest)
or the back-end(supertest).

\subsection{Changes and Adjustments}
\label{sec:orgfb7ce11}

The initial phase of development was accompanied by a few unforeseen challenges
and insights that required changes:

\begin{itemize}
\item Design Alterations: The initial ER schema underwent several
iterationschanges to match the requirements while maintaining it's
simplicity.

\item Technology Adjustments: Decisions regarding the tools and libraries were
refined based on compatibility and performance considerations; We did not
originally know we would choose jest, supertest or gulp.
\end{itemize}


\subsection{Challenges and Overcoming Them}
\label{sec:orgc7fe510}

Phase-1 was not without its hurdles:

\begin{itemize}
\item Integration Challenges with Gulp: The integration required a deep
understanding of the tool and its plugins. This was overcome through
extensive documentation review and experimentation.

\item Security Concerns: Ensuring a secure design required an attentive
approach, this was achieved through following best practices like password
hashing and then using the appropriate libraries to deal with these
nuances.
\end{itemize}


\subsection{Lessons Learned}
\label{sec:org483978b}
Key takeaways from Phase-1 include:

\begin{itemize}
\item The Importance of Planning: Comprehensive planning played a pivotal role
in keeping the project on track.

\item History tracking: code change tracking tools like GitHub fostered a
cohesive development environment to review and track the project and it's
changes over time.

\item Emphasis on Quality: A consistent focus on code quality, security, and
usability ensured a productset of deliverables aligned with high standards.
\end{itemize}


\subsection{Conclusion}
\label{sec:orgb749078}

Phase-1 of the project has set the stage for a well-architected, secure, and
user-centric application. The team's commitment to best practices, innovation,
and continuous improvement has not only led to the successful completion of this
phase but also paved the way for future success. The lessons gleaned will
continue to guide the development as we move forward, with an eye on delivering
a product that stands out in terms of quality, functionality, and design.
\end{document}